Verifying Demonstrations

### 2018-11-28 paper/verifiability-analysis.tex
Adapts verifiability analysis to \corr

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \pi_\pid, \pi_{\wid})\)) are committed to the ledger and 
available from a public and permanent storage (see 
\cref{fig:ProtocolOverview}).
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).
(As these are the main properties of distributed ledgers, we do not elaborate 
further.)

\Cref{UniversalVerif} includes that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\pi_\pid,
\pi_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger and storage; but universal 
verifiability also depends on the eligibility verification, which we will 
discuss next.

>>>>

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
available from a public and permanent storage (see 
\cref{fig:ProtocolOverview}).
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).
(As these are the main properties of distributed ledgers, we do not elaborate 
further.)

\Cref{UniversalVerif} includes that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_\pid,
\corr_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger and storage; but universal 
verifiability also depends on the eligibility verification, which we will 
discuss next.
